Poster Data Analysis

### 2018-09-17 notebooks/poster_analysis.Rmd
added text
added stats for qnr genes

@@

## Heatmap plot
This plot represents the individual resistance mechanisms (x-axis) present in each isolate (y-axis), for each animal species (colors) and sequence type (dendrogram). Grey squares represent genes/mutations that ARIBA flagged as bad quality in their report. Dark color indicates presence, while the light color indicates absence. Part of the code below is taken from https://gist.github.com/scwatts/8c32d8f6dc44e352d89ae3de5f3a1125.
```{r fig.height=30, fig.width=10, message=FALSE, warning=FALSE}
# Adjust MLST data frame
sequence_types_adjusted <- mlst_results %>%
  mutate_all(funs(gsub("\\*", "", .))) %>%
  select(-ST)

>>>>

### Percent qnr genes
The total percentage of qnr genes identified with ARIBA.
```{r}
resfinder_results %>%
  select_at(.vars = vars("qnrA1","qnrB19",
                         "qnrB6","qnrB60",
                         "qnrS1","qnrS2",
                         "qnrS4")) %>%
  mutate(total = rowSums(.),
         result = if_else(total != 0, 1, 0)) %>%
  group_by(result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 0, "Absent", "Present")) %>%
  spread(result, n) %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr))
```

@@

## Heatmap plot
This plot represents the individual resistance mechanisms (x-axis) present in each isolate (y-axis), for each animal species (colors) and sequence type (dendrogram). Grey squares represent genes/mutations that ARIBA flagged as bad quality in their report. Dark color indicates presence, while the light color indicates absence. Part of the code below is taken from https://gist.github.com/scwatts/8c32d8f6dc44e352d89ae3de5f3a1125. The dendrogram was created by calculating the distance between each allele in the MLST scheme (Escherichia coli #1), and then use the UPGMA method to calculate the dendrogram.
```{r fig.height=30, fig.width=10, message=FALSE, warning=FALSE}
# Adjust MLST data frame
sequence_types_adjusted <- mlst_results %>%
  mutate_all(funs(gsub("\\*", "", .))) %>%
  select(-ST)
